### 2019-01-18 README.rmd
remotes pkg to install dev version - resolves #26

Development versions can be installed from GitHub:
```{r eval=FALSE}
devtools::install_github("corybrunson/ggalluvial", build_vignettes = TRUE)
```
The
[optimization branch](https://github.com/corybrunson/ggalluvial/tree/optimization) contains a development version with experimental functions to reduce the number or area of alluvial overlaps (see issue [#6](https://github.com/corybrunson/ggalluvial/issues/6)). Install it as follows:
```{r eval=FALSE}
devtools::install_github("corybrunson/ggalluvial", ref = "optimization")
```

>>>>

Development versions can be installed from GitHub:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", build_vignettes = TRUE)
```
The
[optimization branch](https://github.com/corybrunson/ggalluvial/tree/optimization) contains a development version with experimental functions to reduce the number or area of alluvial overlaps (see issue [#6](https://github.com/corybrunson/ggalluvial/issues/6)). Install it as follows:
```{r eval=FALSE}
remotes::install_github("corybrunson/ggalluvial", ref = "optimization")
```
